\begin{ntheorem}{: Baby Rudin 6.17}
	Let \(f:[a,b]\to\R\) be bounded, and \(\alpha:[a,b]\to\R\) be differentiable and monotone increasing. Suppose \(\alpha'\in\mc{R}[a,b]\). Then \(f\in\mc{R}_{\alpha}[a,b]\iff f\alpha'\in\mc{R}[a,b]\), and if so 
	\begin{equation*}
		\int_a^b f \, d\alpha=\int_a^b f\alpha' \, dx.
	\end{equation*}
\end{ntheorem}

\begin{proof}
	\textbf{Step-1}: It suffices to show that 
	\begin{equation*}
		\ol{\int_a^b}f \, d\alpha=\ol{\int_a^b} f\alpha' \, dx\quad\text{and}\quad \ul{\int_a^b}f \, d\alpha=\ul{\int_a^b} f\alpha' \, dx.
	\end{equation*}
	We will prove the first equality, and the second one is left as an exercise.
	
	\medskip
	
	\textbf{Step-2}: Since \(\alpha'\in\mc{R}[a,b]\) for all \(\eps>0\), there exists \(\mc{P}\) (of \([a,b]\)) such that \(U(\mc{P},\alpha')-L(\mc{P},\alpha')<\eps\). This inequality continues to hold for every refinement \(\mc{P}'\) of \(\mc{P}\).
	
	\medskip
	
	We have \(U(\mc{P},\alpha')-L(\mc{P},\alpha')=\displaystyle\sum_{i=1}^{n}(A_i-a_i)\Delta x_i\), where \(A_i:=\sup\{\alpha'(x)\st x\in[x_{i-1},x_i]\}\), and \(a_i:=\inf\{\alpha'(x)\st x\in[x_{i-1},x_i]\}\). By the Mean Value Theorem for each \(i=1,\dots, n\), there exists \(t_i\in[x_{i-1},x_i]\) such that \(\Delta\alpha_i=\alpha'(t_i)\Delta x_i\). Now, this suggests \(\displaystyle \ol{\int_a^b}f \, d\alpha=\ol{\int_a^b} f\alpha' \, dx\), but we need to be careful:
	
	\medskip
	
	For every \(s_i\in [x_{i-1},x_i]\), we have \(|\alpha'(s_i)-\alpha'(t_i)|\leq A_i-a_i\), so \(\displaystyle\sum_{i=1}^n|\alpha'(s_i)-\alpha'(t_i)|\Delta x_i\leq \displaystyle\sum_{i=1}^n(A_i-a_i)\Delta x_i\) for \emph{every} choice of \(s_i\in [x_{i-1},x_i]\), \(1\leq i\leq n\). Let \(K:=\sup_{x\in [a,b]}{|f|}\), then
	\begin{equation}
		\sum_{i=1}^n |f(s_i)\alpha'(s_i)\Delta x_i-f(s_i)\alpha'(t_i)\Delta x_i|\leq K\eps.\label{sup bound}
	\end{equation}
	Hence, 
	\begin{equation*}
		\sum_{i=1}^n f(s_i)\Delta\alpha_i\leq \sum_{i=1}^n f(s_i)\alpha'(s_i)\Delta x_i+Ke\leq U(\mc{P},f\alpha')+K\eps.
	\end{equation*}
	
	\medskip
	
	Recall that if \(|a+b|\leq c\), then \(a\leq b+c\) and \(b\leq a+c\).
	\begin{note}
		Whenever we have an inequality, we might wonder whether it is ``sharp" or ``tight", meaning it is equality or the closest to equality as possible.
	\end{note}
	
	Taking the supremum of \(s_i\in[x_{i-1},x_i]\), \(i=1,\dots, n\), we conclude 
	\begin{equation*}
		U(\mc{P},f,\alpha)=\sum_{i=1}^n M_i\Delta\alpha_i\leq U(\mc{P},f\alpha')+K\eps.
	\end{equation*}
	Hence, 
	\begin{equation*}
		\ol{\int_a^b}f \, d\alpha\leq U(\mc{P},f,\alpha)\leq U(\mc{P},f\alpha')+K\eps,
	\end{equation*}
	i.e., for every \(\eps\), we found some partition \(\mc{P}\) that makes the inequality hold. Recall that it also holds for every refinement \(\mc{P}'\) of \(\mc{P}\).
	
	\medskip
	
	How can we make this inequality be as close to equality as possible (how much strength can we squeeze out of the inequality?) Taking the infimum over all refinements \(\mc{P}'\) of \(\mc{P}\), we have 
	\begin{equation*}
		\ol{\int_a^b}f \, d\alpha\leq \int_{\mc{P}'} U(\mc{P}',f\alpha')+K\eps.
	\end{equation*}
	Since we are considering a more strict set of partitions, will this give us the infimum we want? The answer is yes: for any non-refinement partition, we union it with \(\mc{P}\) to get a refinement, i.e., for all \(\eps>0\), \(\displaystyle\ol{\int_a^b}f \, d\alpha\leq \ol{\int_a^b}f \alpha' \, dx+K\eps\implies \ol{\int_a^b}f \, d\alpha\leq \ol{\int_a^b}f \alpha' \, dx\). The other three inequalities can be done as an exercise after the following note:
	\begin{note}
		For the inequality 
		\begin{equation*}
			\ol{\int_a^b}f \, d\alpha\geq \ol{\int_a^b}f \alpha' \, dx,
		\end{equation*}
		from \cref{sup bound}, we get 
		\begin{equation*}
			\sum_{i=1}^nf(s_i)\alpha'(s_i)\Delta x_i\leq \sum_{i=1}^n f(s_i)\Delta\alpha_i+K\eps,
		\end{equation*}
		and so on.
	\end{note}
\end{proof}